Paper Summary Assignment

### 2024-11-05 Paper_Summary.Rmd
Starting registered report

# Generate data for each vial/cage (for loops are harder in R than in Python in my opinion!)
for (i in 1:n_vials) {
  # Simple arena
  activity_data <- rbind(activity_data, data.frame(
    female_type = "large",
    arena_type = "simple",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 + mean_diff_simple/2, sd = sd_diff)
  ))
  activity_data <- rbind(activity_data, data.frame(
    female_type = "small",
    arena_type = "simple",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 - mean_diff_simple/2, sd = sd_diff)
  ))

>>>>

# Generate data for each vial/cage (For loops are harder in R than in Python in my opinion!)
for (i in 1:n_vials) {
  # Simple arena
  activity_data <- rbind(activity_data, data.frame(
    female_type = "large",
    arena_type = "simple",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 + mean_diff_simple/2, sd = sd_diff)
  ))
  activity_data <- rbind(activity_data, data.frame(
    female_type = "small",
    arena_type = "simple",
    vial_cage_id = i,
    activity_score = rnorm(1, mean = 10 - mean_diff_simple/2, sd = sd_diff)
  ))
